---
title: "da_proj_india"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readr)
library(ROCR)
library(PerformanceAnalytics)
library(e1071)
library(caret)
library(gbm)
library(corrplot)
library(ggcorrplot)
library(MASS)
library(rpart)
library(caTools)
library(naivebayes)
library(class)
library(ISLR)
library(glmnet)
library(Hmisc)
library(funModeling)
library(pROC)
library(randomForest)
library(klaR)
library(scales)
library(cluster)
library(factoextra)
library(DataExplorer)
library(ClustOfVar)
library(GGally)
library(DescTools)
```

###Loading datasets for Indian cities (all have same format)

```{r}
setwd("C:\\Users\\tarun\\Desktop\\da_proj")
df_bangalore <- read.csv("Bangalore.csv")
df_chennai <- read.csv("Chennai.csv")
df_delhi <- read.csv("Delhi.csv")
df_hyderabad <- read.csv("Hyderabad.csv")
df_mumbai <- read.csv("Mumbai.csv")
```


###Checking %null values
```{r}
print("Bangalore dataset missing values")
plot_missing(df_bangalore)
print("Chennai dataset missing values")
plot_missing(df_chennai)
print("Delhi dataset missing values")
plot_missing(df_delhi)
print("Hyderabad dataset missing values")
plot_missing(df_hyderabad)
print("Mumbai dataset missing values")
plot_missing(df_mumbai)
```


#Since there are no missing values, moving on to PCA
#For Bangalore
```{r}
res_bangalore <- prcomp(df_bangalore[c("Price","No..of.Bedrooms","Area")], scale. = T)
res_bangalore$rotation <- -1*res_bangalore$rotation
res_bangalore$rotation
```

```{r}
res_bangalore$x <- -1*res_bangalore$x
head(res_bangalore$x)
```

```{r}
biplot(res_bangalore)
```
#Since biplot doesnt show any clear depiction for each of the data, it is not displayed for the other cities.


```{r}
var_exp_bangalore <- res_bangalore$sdev^2 / sum(res_bangalore$sdev^2)
var_exp_bangalore
```

#1st component explains 64.86% of total variance, 2nd component explains 26.95% of total variance and 3rd component explains 8.18%


#scree plot
```{r}
qplot(c(1:3), var_exp_bangalore) + 
  geom_line() + 
  xlab("Principal Component") + 
  ylab("Variance Explained") +
  ggtitle("Scree Plot Bangalore") +
  ylim(0, 1)
```

#For Chennai
```{r}
res_chennai <- prcomp(df_chennai[c("Price","No..of.Bedrooms","Area")], scale. = T)
res_chennai$rotation <- -1*res_chennai$rotation
res_chennai$rotation

```



```{r}
res_chennai$x <- -1*res_chennai$x
head(res_chennai$x)
```


```{r}
var_exp_chennai <- res_chennai$sdev^2 / sum(res_chennai$sdev^2)
var_exp_chennai
```
```{r}
qplot(c(1:3), var_exp_chennai) + 
  geom_line() + 
  xlab("Principal Component") + 
  ylab("Variance Explained") +
  ggtitle("Scree Plot Chennai") +
  ylim(0, 1)
```


#For Delhi
```{r}
res_delhi <- prcomp(df_delhi[c("Price","No..of.Bedrooms","Area")], scale. = T)
res_delhi$rotation <- -1*res_delhi$rotation
res_delhi$rotation
```


```{r}
res_delhi$x <- -1*res_delhi$x
head(res_delhi$x)
```


```{r}
var_exp_delhi <- res_delhi$sdev^2 / sum(res_delhi$sdev^2)
var_exp_delhi
```


```{r}
qplot(c(1:3), var_exp_delhi) + 
  geom_line() + 
  xlab("Principal Component") + 
  ylab("Variance Explained") +
  ggtitle("Scree Plot Delhi") +
  ylim(0, 1)
```


#For Hyderabad
```{r}
res_hyderabad <- prcomp(df_hyderabad[c("Price","No..of.Bedrooms","Area")], scale. = T)
res_hyderabad$rotation <- -1*res_hyderabad$rotation
res_hyderabad$rotation
```


```{r}
res_hyderabad$x <- -1*res_hyderabad$x
head(res_hyderabad$x)
```


```{r}
var_exp_hyderabad <- res_hyderabad$sdev^2 / sum(res_hyderabad$sdev^2)
var_exp_hyderabad
```

```{r}
qplot(c(1:3), var_exp_hyderabad) + 
  geom_line() + 
  xlab("Principal Component") + 
  ylab("Variance Explained") +
  ggtitle("Scree Plot Hyderabad") +
  ylim(0, 1)
```


#For Mumbai
```{r}
res_mumbai <- prcomp(df_mumbai[c("Price","No..of.Bedrooms","Area")], scale. = T)
res_mumbai$rotation <- -1*res_mumbai$rotation
res_mumbai$rotation
```


```{r}
res_mumbai$x <- -1*res_mumbai$x
head(res_mumbai$x)
```

```{r}
var_exp_mumbai <- res_mumbai$sdev^2 / sum(res_mumbai$sdev^2)
var_exp_mumbai
```

```{r}
qplot(c(1:3), var_exp_mumbai) + 
  geom_line() + 
  xlab("Principal Component") + 
  ylab("Variance Explained") +
  ggtitle("Scree Plot Mumbai") +
  ylim(0, 1)
```


